---
title: "Portfoliomanagement and Financial Analysis - Assignment 7"
subtitle: "Submit until Monday 2020-11-23, 13:00"
author: "Winder, Anna-Sophie"
output: html_notebook
---
  
```{r setup}
#remotes::install_github("braverock/FactorAnalytics",  build_vignettes = TRUE, force = TRUE)
pacman::p_load(tidyverse,tidyquant,FFdownload,FactorAnalytics,PerformanceAnalytics)
install.packages("psych")
library("psych")
```

**Please** remember to put your assignment solutions in `rmd` format using **many** chunks and putting readable text in between, similar to my examples given in Research Methods and Assignment 1!

For all exercises: Please use the Assignment-Forum to post your questions, I will try my best to help you along!

## Exercise 1: Analysing the CAPM  

In this exercise we want to estimate the CAPM. Please read carefully through the two documents provided (right hand side: files). Then we start to collect the necessary data:
  
a) From Datastream get the last 10 years of data from the 100 stocks of the S&P100 using the list `LS&P100I` (S&P 100): total return index (RI) and market cap (MV)
b) Further import the Fama-French-Factors from Kenneth Frenchs homepage (monthly, e.g. using `FFdownload`). From both datasets we select data for the last (available) 60 months, calculate returns (simple percentage) for the US-Stocks and eliminate those stocks that have NAs for this period.
c) Now subtract the risk-free rate from all the stocks. Then estimate each stocks beta with the market: Regress all stock excess returns on the market excess return and save all betas (optimally use `mutate` and `map` in combination with `lm`). Estimate the mean-return for each stock and plot the return/beta-combinations. Create the security market line and include it in the plot! What do you find?
d) In a next step (following both documents), we sort the stocks according to their beta and build ten value-weighted portfolios (with more or less the same number of stocks). Repeat a) for the ten portfolios. What do you observe?
e) In the third step you follow page 6-8 of the second document and estimate the second-pass regression with the market and then market & idiosyncratic risk. What do you observe? Present all your results in a similar fashion as in the document.

## Exercise 2: Performance Evaluation I

Read Chapter 24 of our book. In this exercise use a Minimum Variance and a Tangecy (maxium Sharpe Ratio) portfolio calculate from your stocks, as well as the S&P500 as a benchmark (Period 2000-01-01 - 2020-01-11). For all three Investment Opportunities imagine you invest 100USD per month into the portfolio. What is the overall return this investment provides you? How much should you have investd at the bginning (one-time investment) to get the eact same overall wealth at the end of 2020? Can you plot both wealth developments over time?

First of all, I am going to download all the crucial data, which we need in order to create the three portfolios. My personal stock choice are Apple, Nividia, Microsoft, American Express, Walmart, Bank of America, Morgan Stanley, Disney, Exxon Mobile. As the benchmark we take the S&P500, regarding to the underling task. 

```{r Choosing my personal set of stocks}
install.packages("FinCal",dependencies=TRUE)
library(timetk,PortfolioAnalytics)
SP500 <- tq_index("SP500")
stock_names <- c("AAPL", "NVDA", "MSFT", "AXP", "WMT", "BAC", "GS","MS", "DIS", "XOM")
```

```{r Return Calculation of the stocks}
stock_returns <-tq_get(x = stock_names,get  = "stock.prices", from = "2000-01-01", to   = "2020-11-18") %>%
    group_by(symbol) %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly")
unique(stock_returns$symbol)

stock_returns_xts <- stock_returns %>%
                      subset( select = c(symbol,date, monthly.returns)) %>% 
                      pivot_wider(names_from = symbol, 
                                  values_from = monthly.returns) %>% 
                      tk_xts(date_var = date, silent = TRUE)
stock_returns_xts
```
```{r Maximum Return}
port <- portfolio.spec(assets=stock_names)%>%
  add.constraint(type="full_investment") %>% #In our approach we use full_investment as our task it is
  add.constraint(type="long_only") %>% #We do not take any short-selling
  add.objective(type="return", name="mean")
port
```

Now I defined the investment constrains for our investments, which is based on our task a full investment constrained, due to the fact that we would like to be fully invested the whole period. The long only constrain comes from the idea that we are just caring about the upper part of the efficient frontier, in order to construct the tangency portfolio, which is the __most efficient__ way to set our 10 stocks together concerning the faced risked. So, in order words the tangency portfolio maximizes the Sharpe Ratio. The second portfolio we have to construct is the Minimum-Variance Portfolio. The _"third"_ portfolio would be an absolute passive strategy we would just invest in the SP500.

```{r }
opt_port <- optimize.portfolio(R=stock_returns_xts, portfolio=port,
                                 optimize_method="ROI", trace=TRUE)
opt_port
```
So, as we see we would make the most money if we would just everything in Nividia. However, we do not look for the maximum return, we look for the maximum return in relation to the taken risk.

```{r}
plot(opt_port, chart.assets=TRUE, main="Maximum Return", 
      xlim=c(0, 0.2), ylim=c(0,0.5))
```
```{r Risk Reward trade of}
chart.RiskReward(opt_port,return.col="mean", risk.col="sd",
                 chart.assets=TRUE, 
                 xlim=c(0, 0.25),
                 main="Maximum Return")
```

```{r}
frontier <- create.EfficientFrontier(R=stock_returns_xts, 
                                       portfolio=port, 
                                       type="mean-StdDev")
chart.EfficientFrontier(frontier, match.col="StdDev", type="l",rf = 0, tangent.line = TRUE, chart.assets = TRUE,)
```
The efficient frontier is the set of optimal portfolios that offer the highest expected return for a defined level of risk or the lowest risk for a given level of expected return. Portfolios that lie below the efficient frontier are sub-optimal because they do not provide enough return for the level of risk.

```{r Tangency Portfolio}
port_tan <- portfolio.spec(assets=stock_names) %>%
  add.constraint(type="full_investment") %>%
  add.constraint(type = "long_only") %>%
  add.objective(type="return", name="mean")
port_tan
```

```{r Constructing the Tangency Portfolio}
init.portf <- portfolio.spec(assets=stock_names)
init.portf <- add.constraint(portfolio=init.portf, type="full_investment")
init.portf <- add.constraint(portfolio=init.portf, type="long_only")
init.portf <- add.objective(portfolio=init.portf, type="return", name="mean")
init.portf <- add.objective(portfolio=init.portf, type="risk", name="StdDev")
init.portf
```
Maximizing the Sharpe Ratio can be formulated as a quadratic programming problem and solved very quickly using optimize_method="ROI". Although "StdDev" was specified as an objective, the quadratic programming problem uses the variance-covariance matrix in the objective function.

The default actin if "mean" and "StdDev" are specified as objectives with optimize_method="ROI" is to maximize quadratic utility. If we want to maximize Sharpe Ratio, we need to pass in maxSR=TRUE to optimize the portfolio, which should lead us to the tangency portfolio.

```{r }
maxSR.lo.ROI <- optimize.portfolio(R=stock_returns_xts, portfolio=init.portf, optimize_methode="ROI", maxSR=TRUE, trace=TRUE)
maxSR.lo.ROI
```
It needed 17 Iterations to come as close as possible to the tangeny portfolio.
We would put a big stake into Walmart, Exxon-Mobil, Disney.
Although the maximum Sharpe Ratio objective can be solved quickly and accurately with optimize_method="ROI", it is also possible or DEoptim. These solvers have the added flexibility of using different methods to calculate the Sharpe Ratio (e.g. we could specify annualized measures of risk and return).

```{r Use random portfolios to run the optimization}
maxSR.lo.RP <- optimize.portfolio(R=stock_returns_xts, portfolio=init.portf, optimize_method="random", search_size=2000, trace=TRUE)
maxSR.lo.RP
chart.RiskReward(maxSR.lo.RP, risk.col="StdDev", return.col="mean")
maxSR.lo.DE <- optimize.portfolio(R=stock_returns_xts, portfolio=init.portf, optimize_method="DEoptim", search_size=2000, trace=TRUE)
maxSR.lo.DE
chart.RiskReward(maxSR.lo.DE, risk.col="StdDev", return.col="mean")
```

The Minmimum Variance Portfolio minimizing the variance of the portfolio

```{r Minimum Variance}
port_minvar <- portfolio.spec(assets=stock_names) %>%
  add.constraint(type="full_investment") %>%
  add.constraint(type = "long_only") %>%
  add.objective(type="risk", name="var")
port_minvar
```

```{r}
opt_minvar <- optimize.portfolio(R = stock_returns_xts,portfolio = port_minvar,
                              optimize_method = "ROI", trace = TRUE)
opt_minvar
```

```{r Plotting the weights}
plot(opt_minvar, chart.assets=TRUE, main="Minimum Variance", 
      xlim=c(0.05, 0.3), ylim=c(0,0.1))
```
So, as we can see we see that we would invest the majority of our capital in Walmart and Exxon Mobile, due to the low standard deviation and quiet interesting we would not invest in Nividia.

```{r}
chart.RiskReward(opt_minvar,return.col="mean", risk.col="sd",
                 chart.assets=TRUE, 
                 xlim=c(0.01, 0.25),
                 main="Minimum Variance")
```

```{r Weight setting for the Portfolios}
wts_tan <- c(0.136, 0.006, 0.000, 0.000, 0.440, 0.018, 0.154, 0.002, 0.000, 0.244)
wts_minvar <- c(0.0241, 0.0000, 0.0615, 0.0000, 0.4551, 0.0000, 0.0000, 0.0000, 0.1094, 0.3499)# Weights from the Minimum Variance Portfolio
```

Portfolio Returns
```{r}
stock_returns

tan_port <- stock_returns %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = monthly.returns, 
                 weights     = wts_tan, 
                 col_rename  = "Return")
tan_port
minvar_port <- stock_returns %>%
    tq_portfolio(assets_col  = symbol, 
                 returns_col = monthly.returns, 
                 weights     = wts_minvar, 
                 col_rename  = "Return")
minvar_port
```
For this task we take the SP500 as the benchmark.
```{r SP500}
bench_returns <- "^GSPC" %>%
    tq_get(get  = "stock.prices",
           from = "2000-01-01",
           to   = "2020-11-17") %>%
    tq_transmute(select     = adjusted, 
                 mutate_fun = periodReturn, 
                 period     = "monthly", 
                 col_rename = "Benchmark")
bench_returns
```
```{r Merging the data together}
ov_tan_port <- left_join(tan_port,bench_returns,by = "date")
ov_minvar_port <- left_join(minvar_port,bench_returns,by = "date")

ov_tan_port
ov_minvar_port
```
```{r Overview for the Tangency Portfolio}
ov_tan_port %>%
    tq_performance(Ra = Return, Rb = Benchmark, 
    performance_fun = table.CAPM)
```

```{r Overview for the Minimum Variance}
ov_minvar_port %>%
    tq_performance(Ra = Return, Rb = Benchmark, 
    performance_fun = table.CAPM)
```
```{r Mean calc}
tan_r <- geometric.mean(ov_tan_port$Return)
minvar_r <- geometric.mean(ov_minvar_port$Return)
bench_r <- geometric.mean(ov_minvar_port$Benchmark)
```

```{r Future Value}
FV_tan <- FV(rate = tan_r, nper = 1:239,pv = 100,pmt = -100,type = 1)
FV_minvar <- FV(rate = minvar_r, nper = 1:239, pv = 100, pmt = -100, type=1)
FV_bench <- FV(rate=bench_r, nper = 1:239, pv = 100, pmt = -100, type = 1)
id <- c(1:239)
as.data.frame(FV_tan)
as.data.frame(id)
as.data.frame(FV_minvar)
as.data.frame(FV_bench)
ov_list <- cbind(id, FV_tan,FV_minvar,FV_bench)
ov_list <- as.data.frame(ov_list)
invest <- ov_list[239,]
invest
```


```{r Ploting the wealth development over time}
ggplot(ov_list, aes(x=id)) + 
  geom_line(aes(y = FV_tan), color = "darkred") + 
  geom_line(aes(y = FV_minvar), color="steelblue", linetype="twodash") +
  geom_line(aes(y=FV_bench), color="pink") +
  ggtitle("Wealth Development")
```
The tangency portfolio performed very good related to the others.

```{r If we would want to get the same amount of money with a one time investment}
PV_tan <- PV(rate = tan_r,nper = 1:239,fv =-invest$FV_tan ,pmt = 0,type = 1)
PV_minvar <- PV(rate =minvar_r, nper=1:239,fv=-invest$FV_minvar,pmt=0,type=1)
PV_bench <- PV(rate=bench_r, nper=1:239, fv=-invest$FV_bench,pmt=0, type=1)
id <- c(1:239)
as.data.frame(PV_tan)
as.data.frame(id)
as.data.frame(PV_minvar)
as.data.frame(PV_bench)
ov_list <- cbind(id, PV_tan,PV_minvar,PV_bench)
ov_list <- as.data.frame(ov_list)
invest <- ov_list[239,]
invest
```
As we see if we would like to make an one time investment, but also the exact same amount of money as if we would invest 100 dollar per month. For the Tangency Portfolio we would need to invest __3734.65__$ for the Minimium Variance Portfolio we would need to invest __4695.70__$ and for the passive strategy S&P500 we would need __5082.05__. So, as we can see that the intrest of intrest effect takes here part and dramatically increases the future value of our investment.

```{r}
ggplot(ov_list, aes(x=id)) + 
  geom_line(aes(y = PV_tan), color = "darkred") + 
  geom_line(aes(y = PV_minvar), color="steelblue", linetype="twodash") +
  geom_line(aes(y=PV_bench), color="pink") +
  ggtitle("One time investment")
```


## Exercise 3: Performance Evaluation II

For the same two portfolios and the appropriate benchmark calculate overall performance measures (Sharpe ratio, M2 [assume a risk-fre rate of 0], Treynor Ratio, Jensen's Alpha and Information ratio). Interpret. Additional do the two market timing regressions (ch 24.4) and see whether your portfolios can "time" the market.



For the Evaluation check the solution in excercise 2 there you can find the CAPM Table, which shows us the Sharpe Ratio, Treynor Ratio, Alpha and the Information Ratio.

Timing Regressions Treynor and Mazuy = __TM__
```{r Timing Regressions}
ts_ov_tan_port <- ts(ov_tan_port)
ts_ov_minvar_port <- ts(ov_minvar_port)
MarketTiming(Ra = ts_ov_tan_port[,2],Rb = ts_ov_tan_port[,3],Rf = 0,method = "TM")
MarketTiming(Ra = ts_ov_minvar_port[,2],Rb = ts_ov_minvar_port[,3],Rf = 0,method = "TM")
```
If the gamma coefficient in the regression is positive, then the estimated equation describes a convex upward-sloping regression "line". Gamma is a measure of the curvature of the regression line. If gamma is positive as the Tangency Portfolio clearly is it indicates that the manager's investment strategy demonstrates market timing ability.


## Exercise 4: Active Portfolio Management

Work through trough the demo `demo(relative_ranking)`. Use what you lear here, form an appropriate opinion on the ranking of your assets and optimize a Minimum Variance and Maximum Sharpe ratio Portfolio. Which one performs better?

demo(relative_ranking)

data(edhec)
```{r}
R <- edhec[,1:4]
```

```{r}
funds <- colnames(R)
```
 #' Construct initial portfolio with basic constraints.
```{r}
init.portf <- portfolio.spec(assets=funds)
```

```{r}
init.portf <- add.constraint(portfolio=init.portf, type="weight_sum", 
                              min_sum=0.99, max_sum=1.01)
```

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
init.portf <- add.constraint(portfolio=init.portf, type="box",min=0.05, max=0.5)
```

```{r}
init.portf <- add.objective(portfolio=init.portf, type="risk", name="StdDev")
```

```{r}

init.portf <- add.objective(portfolio=init.portf, type="return", name="mean")

init.portf
```
> #' Here we express views on the relative rank of the asset returns.

```{r}
asset.rank <- c(2, 3, 1, 4)

```


> #' Use Meucci Fully Flexible Views framework to express views on the relative
> #' order of asset returns.
> #' Define prior probabilities.

```{r}
p <- rep(1 / nrow(R), nrow(R))
```

> #' Express view on the relative ordering of asset returns

```{r}
m.moments <- meucci.ranking(R, p, asset.rank)

```


 #' Express views using the method described in Almgren and Chriss, 
> #' "Portfolios from Sorts".

```{r}
 ac.moments <- list()

ac.moments
```

```{r}
ac.moments$mu <- ac.ranking(R, asset.rank)
```

> # Sample estimate for second moment

```{r}
ac.moments$sigma <- cov(R)
```

> #' Generate random portfolios for use in the optimization.

```{r}
rp <- random_portfolios(init.portf, 5000)

rp
```
> #' Run the optimization using first and second moments estimated from 
> #' Meucci's Fully Flexible Views framework using the moments we calculated


```{r}
opt.meucci <- optimize.portfolio(R, 
                                 init.portf,
                                 optimize_method="random", 
                                 rp=rp, 
                                 trace=TRUE,
                                 momentargs=m.moments)

opt.meucci


```

> #' Run the optimization using first moment estimated based on Almgren and Chriss, 
> #' "Portfolios from Sorts". The second moment uses the sample estimate.

```{r}
opt.ac <- optimize.portfolio(R,
                             init.portf,
                             optimize_method="random",
                             rp=rp,
                             trace=TRUE,
                             momentargs=ac.moments)

opt.ac

```
> #' For comparison, run the optimization using sample estimates for first and 
> #' second moments.

```{r}
opt.sample <- optimize.portfolio(R, 
                                 init.portf, 
                                 optimize_method="random", 
                                 rp=rp,
                                 trace=TRUE)
opt.sample

```


> #' Here we plot the optimal weights of each optimization.

```{r}
chart.Weights(combine.optimizations(list(meucci=opt.meucci, 
                                           ac=opt.ac,
                                           sample=opt.sample)), 
                
              
ylim=c(0,1), plot.type="barplot")

```
> #' Here we define a custom moment function to estimate moments based on 
> #' relative ranking views.
> #' Asset are ranked according to a momentum or reversal view based on the 
> #' previous n periods.

```{r}
moment.ranking <- function(R, n=1, momentum=TRUE, method=c("meucci", "ac")){
  
# Moment function to estimate moments based on relative ranking of 
# expected returns.
  
method <- match.arg(method)
   
   # Use the most recent n periods of returns
   tmpR <- apply(tail(R, n), 2, function(x) prod(1 + x) - 1)
   
   if(momentum){
     # Assume that the assets with the highest return will continue to outperform
     asset.rank <- order(tmpR)
   } else {
# Assume that the assets with the highest return will reverse
asset.rank <- rev(order(tmpR))
}
switch(method,
meucci = {
            # Meucci Fully Flexible Views framework
            # Prior probabilities
           p <- rep(1 / nrow(R), nrow(R))
            
            # Relative ordering view
           moments <- meucci.ranking(R, p, asset.rank)
          },
          ac = {
            # Almgren and Chriss Portfolios from Sorts
            moments <- list()
            moments$mu <- ac.ranking(R, asset.rank)
            # Sample estimate for second moment
            moments$sigma <- cov(R)
         }
   )
   return(moments)
 }


opt.bt.meucci
```

> #' Here we run out of sample backtests to test the out of sample performance using the different frameworks to express our views on relative asset return ranking.

```{r}
pt.bt.meucci <- optimize.portfolio.rebalancing(R, init.portf, 
                                               optimize_method="random",  
                                               rebalance_on="quarters", 
                                               training_period=100,
                                               rp=rp,
                                               momentFUN="moment.ranking",
                                               n=2,
                                               momentum=TRUE,
                                               method="meucci")
pt.bt.meucci

```
```{r}
opt.bt.ac <- optimize.portfolio.rebalancing(R, init.portf, 
optimize_method="random", 
rebalance_on="quarters", 
rp=rp,
momentFUN="moment.ranking",
n=2,
momentum=TRUE,
method="ac")
```

```{r}

opt.bt.sample <- optimize.portfolio.rebalancing(R, init.portf, 
                                                 optimize_method="random", 
                                                 rebalance_on="quarters", 
                                                 training_period=100,
                                                 rp=rp)
```

> #' Compute returns and chart performance summary.

```{r}
ret.meucci <- Return.portfolio(R, extractWeights(opt.bt.meucci))
```

```{r}
ret.ac <- Return.portfolio(R, extractWeights(opt.bt.ac))
```

```{r}
ret.sample <- Return.portfolio(R, extractWeights(opt.bt.sample))
```

```{r}
ret <- cbind(ret.meucci, ret.ac, ret.sample)
```

```{r}
colnames(ret) <- c("meucci.rank", "ac.rank", "sample")
```

```{r}
charts.PerformanceSummary(ret, main="Ranking Views Performance")
```





